\documentclass[xcolor=dvipsnames]{beamer}
%\documentclass{beamer}
%\documentclass[table]{beamer}



%xetex
\usefonttheme{professionalfonts}

\usepackage{xltxtra} % loads fixltx2e, etex, fontspec, xunicode …
\usepackage{array, color, enumerate, fixmath, gensymb, graphicx, graphics,
    icomma, listings, mathcomp, mathtools, mathdots, multirow, ngerman,
    nicefrac, placeins, rotating, tabularx, units, xtab, lipsum}
\usepackage[math-style=ISO]{unicode-math}

% fonts
\setsansfont[Mapping=tex-text]{Komika Text} % normal font
\newcommand{\mschrift}{XITS Math} % math font
\setmathfont[Scale=MatchUppercase]{\mschrift} % proportion math/normal, orientation: uppercase
\setmathfont[Scale=MatchUppercase, range=\mathit/{Latin, latin}->\mathsfit]{\mschrift} %sans
\setmathfont[range=\mathup/{num}]{Komika Text} %numbers in math

% babel replacement
\usepackage{polyglossia}
\setdefaultlanguage[spelling=new, latesthyphen=true]{german}

% settings
\usetheme{Frankfurt}
\usecolortheme[light=false,invertblockcolor=true,maincolor=blue]{solarized}
\setbeamertemplate{navigation symbols}{}

% logo
% \pgfdeclareimage[height=0.5cm]{university-logo}{university-logo-filename}
% \logo{\pgfuseimage{university-logo}}
%xetex end



% titlepage information
\title{Test Solarized}
\subtitle{}
\author{Stephan~Porz}
\institute[Universität Bonn]{}
\date[]{}



\begin{document}

%fontsize
%     \tiny
%     \scriptsize
%     \footnotesize
%     \small
%     \normalsize
%     \large
%     \Large
%     \LARGE
%     \huge
%     \Huge

\begin{frame}[plain]
    \titlepage
\end{frame}



%\begin{frame}{}
\begin{frame}{Contents}
    \tableofcontents
\end{frame}



\section{Section 1}
\subsection{Subsection 1}
\begin{frame}{Page 1}
    This is some text.
    \begin{itemize}
        \item This is item 1
        \item This is item 2
        \begin{itemize}
            \item Second intend
        \end{itemize}			
        \item And another item...
    \end{itemize}
    Even more text\footnote{Stuff you really should not be able to read.}.
\end{frame}

\begin{frame}{Page 2}
    \begin{block}{This is important}
        Text in the block.\\
	Second line in the block.
    \end{block}
    \begin{exampleblock}{Just an illustrative example}
        This is an example of block. \\
	Go no further!
    \end{exampleblock}
    \begin{alertblock}{This is the hard stuff}
        So hard, you can't miss it! \\
	Exclamation mark!11!1oneleven11!
    \end{alertblock}
\end{frame}


\subsection{Subsection 2}

\begin{frame}{Page 3}
    Nothing to see here. \\
    Move along!
\end{frame}



\section{Section 2}
\subsection{Subsection 3}
\begin{frame}{Page 4}
    You shouldn't be here!
\end{frame}



%\section*{}
%\begin{frame}{}
\begin{frame}{Contents}
    \tableofcontents
\end{frame}

\end{document}
